Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-06 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
references update, references.bib created

---
title: "Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy"
author: "Aidan Jackson, Frank Liu, Sam Temlock, Haoyu Zhang"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

# References

>>>>

---
title: "Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy"
author: "Aidan Jackson, Frank Liu, Sam Temlock, Haoyu Zhang"
output:
  pdf_document: default
  html_document:
    df_print: paged
bibliography: references.bib
nocite: '@*'
---

@@

\pagebreak
# References
